Thank you, next: partner turnover elevates benefits of mutualism for an ant-tended plant

### 2023-08-15 Manuscript/ant_cactus_AmNat.tex
manuscript

Defensive ant-plant mutualisms -- where plants provide food and/or housing to ants that in turn defend them from enemies -- are widespread interactions that offer valuable model systems for the ecology and evolution of mutualism \citep{Bronstein1998, Bronstein2006}. 
Extrafloral nectar (EFN) bearing plants can serve as dietary resources that promote ant abundance and colony size \citep{Byk2011, Ness2009, Ness2006}.
Presence of defensive ant partners is often linked to herbivory reduction \citep{Trager2010, Rudgers2010} and demographic advantages for the plant partner \citep{Baez2016}.
\tom{These interactions are almost entirely studied from the perspective of plant fitness \citep{Bronstein1994,Bronstein1998}, with little recorded about the impacts on ant fitness \citep{Lanan2013}.}{Here is a good example of something to avoid. You are highlighting a gap that your paper actually does not fill. Never do this in an Intro, sometimes it can be useful in a discussion as a future direction.}
Defensive ant-plant mutualisms are commonly multi-species, where a guild of ant partner species share, and often compete for, a plant mutualist \citep{Bronstein1998, Beattie1985, Trager2010, Agrawal1998}.
Ant partners can vary in their ability to deter herbivores \citep{bruna2004}, and visitation by low quality ant partners can prevent visitation by higher quality partners, consequently causing a reduction in fitness through missed opportunity costs \citep{Fraser2001, Frederickson2005}.
\tom{Another source of temporal variation is succeptibility to herbivory can also vary significantly throughout the life stages of the plant \citep{Boege2005}, suggesting that the order and timing of successive partners is important to the effectiveness of ant partners.
Temporal dynamics of partner visitation therefore have important impacts on the fitness of the plant partners in these interactions \citep{Barton2010, Boege2005, Fonseca2003}.}{I think you are mixing two ideas here: ontogenetic variation in ant-plant associations (eg directional turnover) and temporal stochasticity that is independent of plant ontogeny. Your study considers both and I think this needs to be set up more clearly.}
\tom{Recently many studies have investigated how partner diversity in these guilds has been shown to lead to either increased plant fitness \citep{Palmer2010, Afkhami2014} or decreased plant fitness (often in more highly specialized interactions) \citep{Barrett2015, Ushio2020}, stressing the importance of considering all ant partners as unique within these guilds. }{I think you need a more effective argument for why your study is necessary given that there are previous studies that have yielded results in both directions.}

>>>>

Defensive ant-plant mutualisms -- where plants provide food and/or housing to ants that in turn defend them from enemies -- are widespread interactions that offer valuable model systems for the ecology and evolution of mutualism \citep{Bronstein1998, Bronstein2006}. 
Extrafloral nectar (EFN) bearing plants can serve as dietary resources that promote ant abundance and colony size \citep{Byk2011, Ness2009, Ness2006}.
Presence of defensive ant partners is often linked to herbivory reduction \citep{Trager2010, Rudgers2010} and demographic advantages for the plant partner \citep{Baez2016}.
Defensive ant-plant mutualisms are commonly multi-species, where a guild of ant partner species share, and often compete for, a plant mutualist \citep{Bronstein1998, Beattie1985, Trager2010, Agrawal1998}.
Ant partners can vary in their ability to deter herbivores \citep{bruna2004}, and visitation by low quality ant partners can prevent visitation by higher quality partners, consequently causing a reduction in fitness through missed opportunity costs \citep{Fraser2001, Frederickson2005}.
Another source of temporal variation is succeptibility to herbivory can also vary significantly throughout the life stages of the plant \citep{Boege2005}, suggesting that the order and timing of successive partners is important to the effectiveness of ant partners.
Temporal dynamics of partner visitation therefore have important impacts on the fitness of the plant partners in these interactions \citep{Barton2010, Boege2005, Fonseca2003}.
\tom{Recently many studies have investigated how partner diversity in these guilds has been shown to impact plant fitness \citep{Palmer2010, Afkhami2014,Barrett2015, Ushio2020}, however, none have considered the combined effects of partner identity, directional partner turnover, and temporal stochasticity on the fitness of plants with a longterm dataset.
